\documentclass[10pt,a4paper]{article}

\usepackage[margin=1.22cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}

% slightly relaxed bullet spacing (for readability)
\setlist[itemize]{leftmargin=*, topsep=1pt, itemsep=1pt}

% slightly more section breathing room
\titlespacing*{\section}{0pt}{6pt}{4pt}
\titleformat{\section}{\bfseries}{}{0em}{}[\titlerule]

\pagenumbering{gobble}

\begin{document}

% HEADER

\begin{center}
    {\Large \textbf{Het Darji}}\


    North York, ON, Canada \textbar{} Open to Hybrid / On-site\


    \href{mailto:darjihet01@gmail.com}{darjihet01@gmail.com} \textbar{}
    647-283-1876 \textbar{}
    \href{https://www.linkedin.com/in/het-darg/}{LinkedIn} \textbar{}
    \href{https://github.com/hetdarji}{GitHub}
\end{center}

\vspace{-2pt}

% SUMMARY
\section*{Professional Summary}

IT Support \& Systems Administrator with 2+ years of Tier 1--2 experience supporting Windows, Microsoft 365, Active Directory / Entra ID, and enterprise network environments. Skilled in troubleshooting hardware, software, identity, and connectivity issues while meeting SLA targets in fast-paced support operations. Experienced with ticketing systems, user lifecycle management, workstation deployment, and end-user assistance. Seeking roles in Technical Support, Service Desk, Helpdesk, or Junior Systems Administration.

% SKILLS
\section*{Technical Skills}

\textbf{Operating Systems:} Windows 10/11, Windows Server, Linux (Ubuntu, CentOS)\\
\textbf{Identity \& Cloud:} Active Directory, Entra ID / Azure AD, Microsoft 365 Admin Center\\
\textbf{Networking:} TCP/IP, DNS, DHCP, VPN, LAN/WAN, Wi-Fi troubleshooting\\
\textbf{Tools:} ServiceNow, SysAid, Jira, Remote Desktop, Intune (basic), MECM (basic)\\
\textbf{Hardware:} Laptops, desktops, printers, docking stations, monitors, peripherals, iOS \& Android\\
\textbf{IT Operations:} Incident management, SLA tracking, onboarding/offboarding, documentation

% EXPERIENCE
\section*{Professional Experience}

\textbf{IT Systems Administrator (Co-op)} \hfill Sep 2024 -- Dec 2024\\
Total Credit Recovery Limited - Toronto, ON

\begin{itemize}
\item  Provided Tier 1–2 support for Windows devices, Microsoft 365, VPN access, and connectivity issues for 200+ on‑site and remote users across multiple departments.
\item Managed user accounts and access in Active Directory and Entra ID including onboarding, password resets, MFA issues, and access troubleshooting.
\item Logged and resolved incidents using SysAid and Jira while meeting SLA targets.
\item Installed and troubleshot desktops, laptops, printers, docking stations, and workplace software.
\item Assisted users with VoIP setup, mailbox access, remote connectivity, and network troubleshooting.
\end{itemize}

\vspace{4pt}

\textbf{Wireless Associate} \hfill Sep 2024 -- Present\\
OSL Wireless, Toronto, ON (Part-time, Weekends)

\begin{itemize}
\item Consistently exceeding annual sales and customer service KPIs with 130\%+ performance.
\item Recognized for strong customer retention and resolving complex service concerns.
\item Assisted customers with smartphone setup, account troubleshooting, and technical guidance.
\item Performed device configuration, SIM activation, data transfer, and software updates.
\end{itemize}

\vspace{4pt}

\textbf{Technical Support Engineer} \hfill Jan 2023 -- Apr 2024\\
Etech Pvt. Ltd. - Gujarat, India

\begin{itemize}
\item Delivered Tier 2 technical support resolving OS, hardware, software, and connectivity issues.
\item Supported Microsoft 365 administration including account setup and permissions.
\item Troubleshot LAN/WAN connectivity, VPN failures, Wi-Fi instability, and remote access issues.
\item Provided remote troubleshooting support using secure remote tools.
\item Assisted with workstation deployments, upgrades, and IT documentation.
\end{itemize}

% EDUCATION
\section*{Education}

\textbf{Post Graduate Diploma - DevOps for Cloud Computing} \hfill 2024--2025\\
Lambton College, Toronto, ON

\textbf{Bachelor of Engineering - Computer Engineering} \hfill 2020--2023\\
Amiraj College, Ahmedabad, India

\textbf{Diploma - Computer Engineering} \hfill 2017--2020\\
Government Polytechnic, Gandhinagar, India

% PROJECT
\vspace{-2pt}
\section*{Projects}

\textbf{Active Directory Domain Services Implementation} \hfill Dec 2024

\begin{itemize}
\item Built an enterprise-style AD lab with multiple domain controllers, DNS, OUs, and Group Policy.
\item Configured VPN-based remote access for secure domain login and testing.
\item Implemented users, security groups, and permissions for enterprise identity control.
\end{itemize}

\end{document}
