\documentclass[10pt,a4paper]{article}

% ---------- BASIC SETUP ----------
\usepackage[margin=1.2cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{fontawesome5}

\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*, topsep=1pt, itemsep=1pt}

% Section spacing
\titlespacing*{\section}{0pt}{4pt}{6pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

% ---------- DOCUMENT ----------
\begin{document}

% ---------- HEADER ----------
\begin{center}
    {\Large \textbf{Het Darji}}\


    North York, ON, Canada \textbar{} Open to Hybrid / On-site\


    \href{mailto:darjihet01@gmail.com}{darjihet01@gmail.com} \textbar{}
    647-283-1876 \textbar{}
    \href{https://www.linkedin.com/in/het-darg/}{LinkedIn} \textbar{}
    \href{https://github.com/hetdarji}{GitHub}
\end{center}

\vspace{-2pt}

% ---------- SUMMARY ----------
\section*{Professional Summary}
IT Support \& Systems Administrator with 2+ years of Tier 1--2 experience supporting enterprise users across Windows, Microsoft 365, Active Directory/Entra ID, and networking environments. Strong troubleshooting and customer service skills with a track record of resolving incidents efficiently, documenting accurately, and maintaining SLA performance. Seeking roles in Technical Support, Service Desk, Helpdesk, or Junior Systems Administration.

% ---------- SKILLS ----------
\section*{Technical Skills}
\textbf{Operating Systems:} Windows 10/11, Windows Server, Linux (Ubuntu/CentOS)\\
\textbf{Identity \& Cloud:} Active Directory, Azure AD / Entra ID, Microsoft 365 Admin Center\\
\textbf{Networking:} TCP/IP, DNS, DHCP, VPN, LAN/WAN, Wi-Fi troubleshooting\\
\textbf{Applications \& Tools:} Microsoft 365, ServiceNow, SysAid, Jira, Remote Desktop, Intune (basic), MECM (basic)\\
\textbf{Hardware \& Devices:} Laptops, desktops, printers, docking stations, monitors, peripherals, iOS \& Android\\
\textbf{IT Operations:} Incident \& request management, SLA tracking, asset management, onboarding/offboarding,\\
\hspace*{0.0em}documentation    



% ---------- EXPERIENCE ----------
\section*{Professional Experience}

\textbf{IT Systems Administrator (Co-op)} \hfill Sep 2025 -- Dec 2025\\
Total Credit Recovery Limited, Toronto, ON
\begin{itemize}
    \item Delivered Tier 1--2 support for Windows 10/11, Microsoft 365, VPN, and connectivity issues for on-site and remote users.
    \item Managed user accounts in \textbf{Active Directory \& Entra ID}, including provisioning, password resets, group membership, and access control.
    \item Resolved incidents and service requests using \textbf{SysAid \& Jira}, consistently meeting SLA targets.
    \item Set up and troubleshot workstations, docking stations, printers, and peripherals across multiple departments.
    \item Assisted with VoIP, remote access, and basic networking (DNS, DHCP, TCP/IP).
    \item Identified recurring issues and proposed improvements that reduced repeat tickets and enhanced user experience.
\end{itemize}

\textbf{Technical Support Engineer} \hfill Jan 2023 -- Apr 2024\\
Etech Pvt. Ltd., Gujarat, India
\begin{itemize}
    \item Provided Tier 2 technical support to 100+ users, resolving escalated hardware, OS, software, and connectivity issues.
    \item Supported Microsoft 365 environments, identity management, and security configurations.
    \item Troubleshot LAN/WAN, Wi-Fi, VPN, and remote access issues, reducing downtime and repeat incidents.
    \item Assisted with system deployments, upgrades, and IT documentation.
    \item Mentored Tier 1 support staff and trained non-technical users on new and existing technologies.
   \item Collaborated with various teams to resolve complex incidents, ensuring timely escalation and high customer satisfaction.
\end{itemize}


% ---------- EDUCATION ----------
\section*{Education}

\textbf{Post Graduate Diploma in DevOps for Cloud Computing} \hfill 2024--2025\\
Lambton College, Toronto, ON

\textbf{Bachelor of Engineering in Computer Engineering} \hfill 2020--2023\\
Amiraj College, Ahmedabad, India

\textbf{Diploma in Computer Engineering} \hfill 2017--2020\\
Government Polytechnic, Gandhinagar, India

% ---------- PROJECTS ----------
\section*{Projects}

\textbf{Active Directory Domain Services (AD DS) Implementation} \hfill Dec 2024\\
Lambton College
\begin{itemize}
    \item Configured AD DS, user accounts, security groups, and Group Policy Objects in a simulated enterprise environment.
    \item Integrated DNS with Active Directory and supported domain controllers and client system onboarding.
    \item Documented procedures for user onboarding, access control, and troubleshooting.
\end{itemize}

\end{document}
